### 2021-07-21 paper/localpsf.tex
edited rational positive definite section based on feedback from Noemi

We extract $\varphi_{x_i}$ for many points $x_i$ by applying $\mathcal{A}$ to Dirac combs associated with ``batches'' of points (Section \ref{sec:get_impulse_response}). To reduce memory usage, all kernels $\varphi_i$ associated with a given batch, $b$, are stored in a single function, $\eta^b$, rather than as distinct functions. A greedy algorithm is used to choose as many points as possible per batch, while ensuring that the points in each batch are not too close to each other, and are not too close to $\partial \Omega$ (Section \ref{sec:greedy_point_selection}). We ensure that the points $x_i$ are well separated from each other by forming a-priori estimates of the supports of the functions $\phi_x$ (Section \ref{eq:mean_and_covariance_estimation}). For the weighting functions, we use the smoothest functions (in a least-squares sense) that interpolate the points $x_i$; constructing the weighting functions requires solving two Poisson PDEs per point $x_i$ (Section \ref{sec:weighting_functions}).
%\begin{itemize}
%\item We extract $\varphi_{x_i}$ for many points $x_i$ by applying $\mathcal{A}$ to Dirac combs associated with ``batches'' of points (Section \ref{sec:get_impulse_response}). To reduce memory usage, all kernels $\varphi_i$ associated with a given batch, $b$, are stored in a single function, $\eta^b$, rather than as distinct functions.
%\item We use a greedy algorithm to choose as many points as possible per batch, while ensuring that the points in each batch are not too close to each other, and are not too close to $\partial \Omega$ (Section \ref{sec:greedy_point_selection}). 
%\item We ensure that the points $x_i$ are well separated from each other by forming a-priori estimates of the supports of the functions $\psi_x$ (Section \ref{eq:mean_and_covariance_estimation}). 
%\item For the weighting functions, we use the smoothest functions (in a least-squares sense) that interpolate the points $x_i$; constructing the weighting functions requires solving two Poisson PDEs per point $x_i$ (Section \ref{sec:weighting_functions}).
%\end{itemize}
The complete algorithm for constructing $\widetilde{\mathcal{A}}$ is shown in Algorithm \ref{alg:construct_Atilde}. The method for evaluating kernel entries of $\widetilde{A}$ is shown in Section \ref{sec:eval_matrix_entries}. The method for converting $\widetilde{\mathcal{A}}$ to H-matrix format is shown in Section \ref{sec:H_matrix_conversion}.

@@

\subsection{Rational positive semi-definite modification}

In many problems of practical interest (e.g., Hessian approximation) $\mathcal{A}$ is symmetric positive semi-definite. However, $\widetilde{\mathbf{A}}$ is generally non-symmetric and indefinite because of errors in the product-convolution approximation. 
This is undesirable. Symmetry and positive semi-definiteness are important properties which should be preserved if possible. Also, lacking these properties may prevent one from using popular and highly effective algorithms, such as the conjugate gradient method, to perform further useful operations involving $\widetilde{\mathbf{A}}$.
In this section we describe a method for modifying $\widetilde{\mathbf{A}}$ to make it symmetric positive semi-definite.

First, we use fast H-matrix addition to symmetrize $\widetilde{\mathbf{A}}$:
$$\widetilde{\mathbf{A}}_\text{sym} := \frac{1}{2}\left(\widetilde{\mathbf{A}} + \widetilde{\mathbf{A}}^T\right).$$
Then we modify $\widetilde{\mathbf{A}}_\text{sym}$ to make it positive semi-definite by forming a rational matrix function of the following form: 
\begin{equation}
\label{eq:rational_matrix_function}
\widetilde{\mathbf{A}}_\text{sym}^+ := c_0 \mathbf{I} + c_1 \widetilde{\mathbf{A}}_\text{sym} + c_2 \left(\widetilde{\mathbf{A}}_\text{sym} + \mu \mathbf{I}\right)^{-1},
\end{equation}
where $\mathbf{I}$ is the identity matrix which has the same shape as $\widetilde{\mathbf{A}}_\text{sym}$. The scalars $c_0$, $c_1$, $c_2$, and $\mu$ are chosen so that the moderate and large positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}^+$ approximately equal the corresponding moderate and large positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$, while the negative and small positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$ are modified so that $\widetilde{\mathbf{A}}_\text{sym}^+$ is positive semi-definite. Later in this section we will explain how $c_0$, $c_1$, $c_2$, and $\mu$ are chosen and how our choice of these scalars affects the spectral properties of $\widetilde{\mathbf{A}}_\text{sym}^+$. Forming $\widetilde{\mathbf{A}}_\text{sym}^+$ requires computing an H-matrix inverse, $\left(\widetilde{\mathbf{A}}_\text{sym} + \mu \mathbf{I}\right)^{-1}$. While explicit computation of matrix inverses should usually be avoided, here it is fine to compute the inverse because $\widetilde{\mathbf{A}}_\text{sym} + \mu \mathbf{I}$ is an H-matrix. There exist fast, stable, scalable, and widely used algorithms for inverting H-matrices \cite{Hmatrixinverse}.

Approximation \eqref{eq:rational_matrix_function} may be written as $\widetilde{\mathbf{A}}_\text{sym}^+ = f(\widetilde{\mathbf{A}}_\text{sym})$, where
\begin{equation}
\label{eq:rational_function_scalar}
f(\lambda) := c_0 + c_1 \lambda + \frac{c_2}{\lambda+\mu}.
\end{equation}
We choose $c_0, c_1, c_2$, and $\mu$, to be the solution to the following system of equations:
\begin{align}
f(0) &= 0 \label{eq:desired_property_1} \\
f'(0) &= 0 \label{eq:desired_property_2} \\
f(\lambda_\text{min}) &= |\lambda_\text{min}| \label{eq:desired_property_3} \\
f(\lambda_\text{max}) &= \lambda_\text{max}, \label{eq:desired_property_4}
\end{align}
where $\lambda_\text{min}$ and $\lambda_\text{max}$ are the smallest and largest eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$, respectively. We also require $\mu > |\lambda_\text{min}|$, so that the pole of $f$ is not in $[\lambda_\text{min},\lambda_\text{max}]$. Note that $\lambda_\text{min} < 0$ since $\widetilde{\mathbf{A}}_\text{sym}$ is indefinite. 
We estimate $\lambda_\text{min}$ and $\lambda_\text{max}$ using the implicitly restarted Lanczos method \cite{lanczos,scipy}, a matrix-free Krylov method. This is fast because computing matrix-vector products with an H-matrix is fast, and because the eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$ do not cluster near $\lambda_\text{min}$ or $\lambda_\text{max}$ (though the eigenvalues may cluster at zero).

Together, equations \eqref{eq:desired_property_1}, \eqref{eq:desired_property_2}, \eqref{eq:desired_property_3},  and \eqref{eq:desired_property_4}, and the condition $\mu > |\lambda_\text{min}|$, imply that $f(0)=0$ is the unique minimum of $f$ on $[\lambda_\text{min},\lambda_\text{max}]$, which implies that $f$ is non-negative on $[\lambda_\text{min},\lambda_\text{max}]$, which implies that  $f(\widetilde{\mathbf{A}}_\text{sym}) = \widetilde{\mathbf{A}}_\text{sym}^+$ is positive semi-definite. The equation $f(0)=0$ implies that the null space of $\widetilde{\mathbf{A}}_\text{sym}^+$ contains the null-space of $\widetilde{\mathbf{A}}_\text{sym}$. This is important when the operator $\mathcal{A}$ has a large (or infinite) dimensional null space, or a spectrum that clusters at zero. Hessians in ill-posed distributed parameter inverse problems typically have both of these properties. The equation $f(\lambda_\text{max})=\lambda_\text{max}$ forces the moderate and large positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}^+$ to be close to the corresponding moderate and large positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$. I.e., $f$ modifies the ``important'' part of the spectrum of $\widetilde{\mathbf{A}}_\text{sym}$ as little as possible. The equation $f(\lambda_\text{min})=|\lambda_\text{min}|$ ensures that the negative eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$, which result from error in the product-convolution approximation, do not get amplified in magnitude by the function $f$. There is a tradeoff: if we choose a larger value for $f(\lambda_\text{min})$, then the positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}^+$ will be closer to the corresponding positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$ (good), but the erroneous negative eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$ will be amplified in magnitude (bad). This is shown in Figure FIG. We find that $f(\lambda_\text{min})=|\lambda_\text{min}|$ is an appropriate balance between these competing interests.

Using the definition of $f$ in \eqref{eq:rational_function_scalar}, and basic calculus and linear algebra, we may write Equations \eqref{eq:desired_property_1}, \eqref{eq:desired_property_2}, and \eqref{eq:desired_property_4} in the following matrix form:
\begin{equation}
\label{eq:rational_3_linear_system}
\begin{bmatrix} 1 & 0 & 1/\mu \\ 0 & 1 & -1/\mu^2 \\ 1 & \lambda_\text{max} & 1/(\lambda_\text{max}+\mu) \end{bmatrix} \begin{bmatrix} c_0 \\ c_1 \\ c_2 \end{bmatrix} = \begin{bmatrix} 0 \\ 0 \\ \lambda_\text{max} \end{bmatrix},
\end{equation}
and we may write Equation \eqref{eq:desired_property_3} as follows: 
\begin{equation}
\label{eq:rational_extra_eq}
\underbrace{c_0 + c_1 \lambda_\text{min} + \frac{c_2}{\lambda_\text{min}+\mu} - |\lambda_\text{min}|}_{g(\mu)} = 0.
\end{equation}
Let $g(\mu)$ denote the left hand side of \eqref{eq:rational_extra_eq}, but with $c_0$, $c_1$, and $c_2$ being the solution of \eqref{eq:rational_3_linear_system} for the given value of $\mu$. I.e., within $g(\mu)$ the quantities $c_0$, $c_1$, and $c_2$ are no longer free variables; they now depend on $\mu$ implicitly through the solution of a linear system. We solve the combined system, \eqref{eq:rational_3_linear_system} and $\eqref{eq:rational_extra_eq}$, by solving the one-dimensional nonlinear root finding problem
\begin{equation}
\label{eq:g_mu_zero}
g(\mu)=0
\end{equation}
with bound $\mu > |\lambda_\text{min}|$ and initial guess $\mu_0 = 2 |\lambda_\text{min}|$. Each evaluation of $g$ requires solving the $3 \times 3$ linear system \eqref{eq:rational_3_linear_system}, and once the solution $\mu$ is found, we solve \eqref{eq:rational_3_linear_system} one more time to get the final values of $c_0$, $c_1$, and $c_2$.
%
%Row 1 corresponds to the condition $f(M)=M$, row 2 corresponds to the condition $f(0)=0$, and row 3 corresponds to the condition $f'(0)=0$. To find the third row of $A$, we used the fact that the derivative of $f$ is given by $$f'(\lambda) = c_1 - \frac{c_2}{(\lambda+\mu)^2}.$$
%
%
%We want $f(\lambda)$ to have the following desirable properties:
%\begin{enumerate}
%	\item $f(\lambda)$ is nonnegative on $[m, M]$.
%	\item $f(\lambda) \approx \lambda$ when $\lambda$ is positive and not small.
%	\item $f(0)=0$ is the minimum of $f(\lambda)$ on $[m, M]$.
%	\item $f(\lambda) \le |\lambda|$ when $\lambda$ is negative.
%\end{enumerate}
%Property 1 ensures that $\widetilde{\mathbf{A}}_\text{sym}^+$ is positive semi-definite. Property 2 ensures that $f$ modifies the ``important'' part of the spectrum of $\widetilde{\mathbf{A}}_\text{sym}$ as little as possible. That is, the part of the spectrum of $\mathcal{A}$ that we expect to be well-approximated by the product-convolution approximation. Property 3 ensures that $\widetilde{\mathbf{A}}_\text{sym}^+$ preserves the null-space (and near null-space) of $\widetilde{\mathbf{A}}_\text{sym}$. This is important because in practice, we often want to approximate operators $\mathcal{A}$ that have a large (possibly infinite) number of zero eigenvalues, and/or a sequence of eigenvalues that clusters at zero. Hessians in ill-posed inverse problems typically have both of these properties. Property 4 ensures that $f$ does not amplify erroneous negative eigenvalues $\widetilde{\mathbf{A}}_\text{sym}$. If $\mathcal{A}$ is positive semi-definite, then eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$ can only be negative because of errors in the product-convolution approximation.

>>>>

We extract $\varphi_{x_i}$ for many points $x_i$ by applying $\mathcal{A}$ to Dirac combs associated with ``batches'' of points (Section \ref{sec:get_impulse_response}). 
%To reduce memory usage, all kernels $\varphi_i$ associated with a given batch, $b$, are stored in a single function, $\eta^b$, rather than as distinct functions. 
A greedy algorithm is used to choose as many points as possible per batch, while ensuring that the points in each batch are not too close to each other, and are not too close to $\partial \Omega$ (Section \ref{sec:greedy_point_selection}). We ensure that the points $x_i$ are well separated from each other by forming a-priori estimates of the supports of the functions $\phi_x$ (Section \ref{eq:mean_and_covariance_estimation}). For the weighting functions, we use the smoothest functions (in a least-squares sense) that interpolate the points $x_i$; constructing the weighting functions requires solving two Poisson PDEs per point $x_i$ (Section \ref{sec:weighting_functions}).
%\begin{itemize}
%\item We extract $\varphi_{x_i}$ for many points $x_i$ by applying $\mathcal{A}$ to Dirac combs associated with ``batches'' of points (Section \ref{sec:get_impulse_response}). To reduce memory usage, all kernels $\varphi_i$ associated with a given batch, $b$, are stored in a single function, $\eta^b$, rather than as distinct functions.
%\item We use a greedy algorithm to choose as many points as possible per batch, while ensuring that the points in each batch are not too close to each other, and are not too close to $\partial \Omega$ (Section \ref{sec:greedy_point_selection}). 
%\item We ensure that the points $x_i$ are well separated from each other by forming a-priori estimates of the supports of the functions $\psi_x$ (Section \ref{eq:mean_and_covariance_estimation}). 
%\item For the weighting functions, we use the smoothest functions (in a least-squares sense) that interpolate the points $x_i$; constructing the weighting functions requires solving two Poisson PDEs per point $x_i$ (Section \ref{sec:weighting_functions}).
%\end{itemize}
The complete algorithm for constructing $\mathcal{A}_\text{pc}$ is shown in Algorithm \ref{alg:construct_Atilde}. The method for evaluating kernel entries of $\Phi_\text{pc}$ is shown in Section \ref{sec:eval_matrix_entries}. The method for converting $\mathcal{A}_\text{pc}$ to H-matrix format is shown in Section \ref{sec:H_matrix_conversion}. The method for modifying the resulting H-matrix to make it symmetric positive semi-definite is shown in Section \ref{sec:make_spd}.

@@

\subsection{Rational positive semi-definite modification}
\label{sec:make_spd}

In many problems of practical interest (e.g., Hessian approximation) $\mathcal{A}$ is symmetric positive semi-definite. However, $\widetilde{\mathbf{A}}$ is generally non-symmetric and indefinite because of errors in the product-convolution approximation. 
This is undesirable. Symmetry and positive semi-definiteness are important properties which should be preserved if possible. Also, lacking these properties may prevent one from using highly effective algorithms, such as the conjugate gradient method, to perform further useful operations involving $\widetilde{\mathbf{A}}$.
In this section we describe a method for modifying $\widetilde{\mathbf{A}}$ to make it symmetric positive semi-definite.

First, we use fast H-matrix addition to symmetrize $\widetilde{\mathbf{A}}$:
$$\widetilde{\mathbf{A}}_\text{sym} := \frac{1}{2}\left(\widetilde{\mathbf{A}} + \widetilde{\mathbf{A}}^T\right).$$
Then we modify $\widetilde{\mathbf{A}}_\text{sym}$ to make it positive semi-definite by forming a rational matrix function of the following form: 
\begin{equation}
\label{eq:rational_matrix_function}
\widetilde{\mathbf{A}}_\text{sym}^+ := c_0 \mathbf{I} + c_1 \widetilde{\mathbf{A}}_\text{sym} + c_2 \left(\widetilde{\mathbf{A}}_\text{sym} + \mu \mathbf{I}\right)^{-1},
\end{equation}
where $\mathbf{I}$ is the identity matrix which has the same shape as $\widetilde{\mathbf{A}}_\text{sym}$. The scalars $c_0$, $c_1$, $c_2$, and $\mu$ are chosen so that the moderate and large positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}^+$ approximately equal the corresponding moderate and large positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$, while the negative and small positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$ are modified so that $\widetilde{\mathbf{A}}_\text{sym}^+$ is positive semi-definite. Later in this section we will explain how $c_0$, $c_1$, $c_2$, and $\mu$ are chosen and how our choice of these scalars affects the spectral properties of $\widetilde{\mathbf{A}}_\text{sym}^+$. In Figure FIG we compare the spectrum of $\widetilde{\mathbf{A}}_\text{sym}$ to that of $\widetilde{\mathbf{A}}_\text{sym}^+$ for different choices of these scalars. Forming $\widetilde{\mathbf{A}}_\text{sym}^+$ requires computing an H-matrix inverse, $\left(\widetilde{\mathbf{A}}_\text{sym} + \mu \mathbf{I}\right)^{-1}$. While explicit computation of matrix inverses should usually be avoided, here it is computationally acceptable because $\widetilde{\mathbf{A}}_\text{sym} + \mu \mathbf{I}$ is an H-matrix. Inversion of H-matrices is a routine procedure which only requires $O(N k^2 \log(N)^2)$ work, where $k$ is the H-matrix rank \cite{Hmatrixinverse}.

Approximation \eqref{eq:rational_matrix_function} may be written as $\widetilde{\mathbf{A}}_\text{sym}^+ = f(\widetilde{\mathbf{A}}_\text{sym})$, where
\begin{equation}
\label{eq:rational_function_scalar}
f(\lambda) := c_0 + c_1 \lambda + \frac{c_2}{\lambda+\mu}.
\end{equation}
We choose $c_0, c_1, c_2$, and $\mu$, to be the solution to the following system of equations:
\begin{subequations}
	\label{eq:four_eq_system}
\begin{align}
f(0) &= 0 \label{eq:desired_property_1} \\
f'(0) &= 0 \label{eq:desired_property_2} \\
f(\lambda_\text{min}) &= |\lambda_\text{min}| \label{eq:desired_property_3} \\
f(\lambda_\text{max}) &= \lambda_\text{max}, \label{eq:desired_property_4}
\end{align}
\end{subequations}
where $\lambda_\text{min}$ and $\lambda_\text{max}$ are the smallest and largest eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$, respectively. We also require $\mu > |\lambda_\text{min}|$, so that the pole of $f$ is not in $[\lambda_\text{min},\lambda_\text{max}]$. Note that $\lambda_\text{min} < 0$ since $\widetilde{\mathbf{A}}_\text{sym}$ is indefinite. 
We estimate $\lambda_\text{min}$ and $\lambda_\text{max}$ using the implicitly restarted Lanczos method \cite{lanczos,scipy}. 
%This is fast because computing matrix-vector products with an H-matrix is fast, and because the eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$ do not cluster near $\lambda_\text{min}$ or $\lambda_\text{max}$ (though the eigenvalues may cluster at zero).

Together, equations \eqref{eq:desired_property_1}, \eqref{eq:desired_property_2}, \eqref{eq:desired_property_3},  and \eqref{eq:desired_property_4}, and the condition $\mu > |\lambda_\text{min}|$, imply that $f(0)=0$ is the unique minimum of $f$ on $[\lambda_\text{min},\lambda_\text{max}]$, which implies that $f$ is non-negative on $[\lambda_\text{min},\lambda_\text{max}]$, which implies that  $f(\widetilde{\mathbf{A}}_\text{sym}) = \widetilde{\mathbf{A}}_\text{sym}^+$ is positive semi-definite. Furthermore, \eqref{eq:desired_property_1} implies that the null space of $\widetilde{\mathbf{A}}_\text{sym}^+$ contains the null-space of $\widetilde{\mathbf{A}}_\text{sym}$. This is important when the operator $\mathcal{A}$ has a large (or infinite) dimensional null space, or a spectrum that clusters at zero. Hessians in ill-posed distributed parameter inverse problems typically have both of these properties. Equation \eqref{eq:desired_property_4} forces the moderate and large positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}^+$ to be close to the corresponding moderate and large positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$. I.e., $f$ modifies the ``important'' part of the spectrum of $\widetilde{\mathbf{A}}_\text{sym}$ as little as possible. Equation \eqref{eq:desired_property_3} ensures that the negative eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$, which result from error in the product-convolution approximation, do not get amplified in magnitude by the function $f$. There is a tradeoff: if we choose a larger value for $f(\lambda_\text{min})$, then the positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}^+$ will be closer to the corresponding positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$ (good), but the erroneous negative eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$ will be amplified in magnitude (bad). This is shown in Figure FIG. We find that $f(\lambda_\text{min})=|\lambda_\text{min}|$ is an appropriate balance between these competing interests.

Solving system \eqref{eq:four_eq_system} is computationally trivial. Using the definition of $f$ in \eqref{eq:rational_function_scalar}, and basic calculus and linear algebra, we may write Equations \eqref{eq:desired_property_1}, \eqref{eq:desired_property_2}, and \eqref{eq:desired_property_4} in the following matrix form:
\begin{equation}
\label{eq:rational_3_linear_system}
\begin{bmatrix} 1 & 0 & 1/\mu \\ 0 & 1 & -1/\mu^2 \\ 1 & \lambda_\text{max} & 1/(\lambda_\text{max}+\mu) \end{bmatrix} \begin{bmatrix} c_0 \\ c_1 \\ c_2 \end{bmatrix} = \begin{bmatrix} 0 \\ 0 \\ \lambda_\text{max} \end{bmatrix},
\end{equation}
and we may write Equation \eqref{eq:desired_property_3} as follows: 
\begin{equation}
\label{eq:rational_extra_eq}
c_0 + c_1 \lambda_\text{min} + \frac{c_2}{\lambda_\text{min}+\mu} - |\lambda_\text{min}| = 0.
\end{equation}
Let 
\begin{equation*}
g(\mu) := c_0(\mu) + c_1(\mu) \lambda_\text{min} + \frac{c_2(\mu)}{\lambda_\text{min}+\mu} - |\lambda_\text{min}|
\end{equation*}
denote the left hand side of \eqref{eq:rational_extra_eq}, but with $c_0(\mu)$, $c_1(\mu)$, and $c_2(\mu)$ being the solution of \eqref{eq:rational_3_linear_system} for the given value of $\mu$. I.e., within $g(\mu)$ the quantities $c_0$, $c_1$, and $c_2$ are no longer free variables; they now depend on $\mu$ implicitly through the solution of a linear system. We solve the combined system, \eqref{eq:rational_3_linear_system} and $\eqref{eq:rational_extra_eq}$, by solving the one-dimensional nonlinear root finding problem
\begin{equation}
\label{eq:g_mu_zero}
g(\mu)=0
\end{equation}
with bound $\mu > |\lambda_\text{min}|$ and initial guess $\mu_0 = 2 |\lambda_\text{min}|$. Each evaluation of $g$ requires solving the $3 \times 3$ linear system \eqref{eq:rational_3_linear_system}, and once the solution $\mu$ is found, we solve \eqref{eq:rational_3_linear_system} one more time to get the final values of $c_0$, $c_1$, and $c_2$.
%
%Row 1 corresponds to the condition $f(M)=M$, row 2 corresponds to the condition $f(0)=0$, and row 3 corresponds to the condition $f'(0)=0$. To find the third row of $A$, we used the fact that the derivative of $f$ is given by $$f'(\lambda) = c_1 - \frac{c_2}{(\lambda+\mu)^2}.$$
%
%
%We want $f(\lambda)$ to have the following desirable properties:
%\begin{enumerate}
%	\item $f(\lambda)$ is nonnegative on $[m, M]$.
%	\item $f(\lambda) \approx \lambda$ when $\lambda$ is positive and not small.
%	\item $f(0)=0$ is the minimum of $f(\lambda)$ on $[m, M]$.
%	\item $f(\lambda) \le |\lambda|$ when $\lambda$ is negative.
%\end{enumerate}
%Property 1 ensures that $\widetilde{\mathbf{A}}_\text{sym}^+$ is positive semi-definite. Property 2 ensures that $f$ modifies the ``important'' part of the spectrum of $\widetilde{\mathbf{A}}_\text{sym}$ as little as possible. That is, the part of the spectrum of $\mathcal{A}$ that we expect to be well-approximated by the product-convolution approximation. Property 3 ensures that $\widetilde{\mathbf{A}}_\text{sym}^+$ preserves the null-space (and near null-space) of $\widetilde{\mathbf{A}}_\text{sym}$. This is important because in practice, we often want to approximate operators $\mathcal{A}$ that have a large (possibly infinite) number of zero eigenvalues, and/or a sequence of eigenvalues that clusters at zero. Hessians in ill-posed inverse problems typically have both of these properties. Property 4 ensures that $f$ does not amplify erroneous negative eigenvalues $\widetilde{\mathbf{A}}_\text{sym}$. If $\mathcal{A}$ is positive semi-definite, then eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$ can only be negative because of errors in the product-convolution approximation.
